---
title: "Lab 10 - Grading the professor, Pt. 2"
author: "Insert your name here"
date: "Insert date here"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidymodels)
library(openintro)
```

### Exercise 1

A one unit increase in a professor's beauty rating leads to a .06 unit increase in their course evaluations. R2 = 3.5%; Adjusted R2 = 3.3%.

```{r model-one}

m_bty <- linear_reg() %>%
  set_engine ("lm") %>%
  fit(score ~ bty_avg, data = evals)

tidy(m_bty)

glance(m_bty)$r.squared
glance(m_bty)$adj.r.squared

```


### Exercise 2

score = bty_avg(.074) + gender(.172)

R2 = 5.9%
Adjusted R2 = 5.5%

```{r model-two}

m_bty_gen <- linear_reg() %>%
  set_engine("lm") %>%
  fit(score ~ bty_avg + gender, data = evals)

tidy(m_bty_gen)

glance(m_bty_gen)$r.squared
glance(m_bty_gen)$adj.r.squared

```


### Exercise 3

Holding gender constant, a one unit increase in a professor's beauty rating predicts a .07 unit increase in their course evaluations. 

Holding beauty constant, male professors tend to receive course evaluations that are .17 points higher than female professors.

### Exercise 4

5.5% of the total variance in course evaluation scores is explained by the professor's beauty and gender.

### Exercise 5


